---
title: "Final Project - Factoring"
output: Group 6 - Jasmine Duong
---

#reading in the aggregated data from Emily
```{r collecting, eval=TRUE}
link='https://github.com/Group-6-542/EmilyRepository/raw/main/mergedGroupDataFinal.csv'

finalData=read.csv(link)
```

#taking out a smaller part of the data
```{r}
subSet = finalData [,c(3:6)]
```

#returns names of columns in this subset
```{r}
names(subSet)
```

```{r}
#install.packages("lavaan", dependencies = TRUE)
```

```{r}
library(lavaan)
```

#conducting a fit CFA factoring analysis
```{r}
model='dem=~ numberOfReturns + avgAGI + casesReported + numberOfPets'

fit<-cfa(model, data = subSet,std.lv=TRUE)
indexCFA=lavPredict(fit)
```

```{r}
library(magrittr)
```

#checking to see the range of the CFA index (not between 0 and 10)
```{r}
indexCFA%>%head(10)
```

#adjusting the CFA index range to be between 0 and 10
```{r}
library(scales)
indexCFANorm=rescale(as.vector(indexCFA), to = c(0, 10))
```

#this is our final index variable
```{r}
finalData$Factoring=indexCFANorm
```

```{r}
library(ggplot2)
```

#plotting this index
```{r}
base=ggplot(data= finalData, aes(x=Factoring))
base+geom_histogram()
```

#plotting against other variables, Number of Returns
```{r}
base=ggplot(data= finalData, aes(x=Factoring, y=numberOfReturns))
base+geom_point()
```

#plotting against other variables, avg AGI
```{r}
base=ggplot(data= finalData, aes(x=Factoring, y=avgAGI))
base+geom_point()
```

#plotting against other variables, Cases Reported
```{r}
base=ggplot(data= finalData, aes(x=Factoring, y=casesReported))
base+geom_point()
```

#plotting against other variables, Number of Pets
```{r}
base=ggplot(data= finalData, aes(x=Factoring, y=numberOfPets))
base+geom_point()
```

#Gives an estimate of the dataframe of this latent variable model
```{r}
evalCFA1=parameterEstimates(fit, standardized =TRUE)
```

#returns the standard deviation and p-value for each column in subset
```{r}
evalCFA1[evalCFA1$op=="=~",c('rhs','std.all','pvalue')]
```

```{r}
evalCFA2=as.list(fitMeasures(fit))
```

#returns the chi-square, degrees of freedom, and p-value for the model (p-value of chi-square greater than 0.05)
```{r}
evalCFA2[c("chisq", "df", "pvalue")] 
```

#caluculates the Tucker-Lewis, incremential fit index (greater than 0.9)
```{r}
evalCFA2$tli
```

#calculates the RMSEA (less than 0.05)
```{r}
evalCFA2[c( 'rmsea.ci.lower','rmsea','rmsea.ci.upper')] 
```

```{r}
#install.packages("semPlot5", dependencies = TRUE)
```

```{r}
library(semPlot)
```

#plots out the diagram of the SEM model, general lineal model
```{r}
semPaths(fit, what='std', nCharNodes=10, sizeMan=8,
         edge.label.cex=1.5, fade=T,residuals = F)
```

